---
title: "Chick Feed Analysis"
author: "Rachael Kawira"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Chick Feed Analysis
#####This Analysis shows how different chicks' weight increased over time and what feed they were using.
#####The data set is one of the already existent datasets on R. An overview of the dataset was done to understand the structure of the data.


```{r chick}
datasets::ChickWeight -> chicken
summary(chicken)
colnames(chicken)
colSums(is.na(chicken))
boxplot(chicken)
```

### Check whether there is is significant difference in chick weight based on the diet. According to this data there is significant difference between the weights based on the diet

```{r anova, echo=FALSE}
anova_result <- aov(weight~Diet,data=chicken)
summary(anova_result)
```

### Check whether the chick weight changes over time maintaining all the other factors and in this case it does

```{r linear, echo=FALSE}
lm(weight ~ Time, data = chicken)
```
### Plot that on a graph to show what it looks like

```{r graph1, echo=FALSE}
install.packages("ggplot2")
library(ggplot2)
ggplot(chicken, aes(x = Time, y = weight)) +
  geom_point(color = "blue") +  # Scatter plot with blue points
  geom_smooth(method = "lm", color = "red", se = FALSE) +  # Adds a red linear regression line without confidence intervals
  labs(title = "Weight vs Time", x = "Time", y = "Weight") +  # Labels for the plot
  theme_minimal()
```
### Proceed to look if there is an effect of time on weight for each diet. With the base diet being diet1, when the time increases by 1 unit chicks on diet 1 increase by 8.75 units, those on diet 2 weigh 16.17 units more than those on diet 1, those on diet3 weigh 26.5 units more than diet 1 and those on diet4 weigh 30.23 more than those on diet1.

```{r linear2, echo=FALSE}
lm(weight ~ Time + Diet, data = chicken)
```
### Check whether there is differences in weight gain over time between individual chicks.
```{r mixed, echo=FALSE}
install.packages("lme4")
library("lme4")
lmer(weight ~ Time + (1 | Chick), data = chicken)
```

### Check whether there is correlation between chick weight and time and to ensure there is no multicolinearity.

```{r corr, echo=FALSE}
cor.test(chicken$weight,chicken$Time)
```
### Finally observe the weight distribution for each diet.

```{r mean, echo=FALSE}
aggregate(weight ~ Diet, data=chicken, summary)
```
